LAGOS lake depth

### 2020-05-04 README.Rmd
point to combined figs and appendix
formatting

## Bathymetry data from thousands of lakes show that difficulty modeling in-lake slope confounds lake depth prediction

@@

Figures: [manuscript/figures.pdf](manuscript/figures.pdf)

>>>>

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Docker Build](https://img.shields.io/badge/Docker%20Image-jsta/bathymetry-green.svg)](https://cloud.docker.com/repository/docker/jsta/bathymetry)

Code and data
for:

**Stachelek et al. In prep**. Bathymetry data from thousands of lakes show that lake depth prediction is confounded by difficulty modeling inlake slope.

@@

Figures: [manuscript/combined.pdf](manuscript/combined.pdf)
